---
title: "Class Project"
subtitle: "Initital Draft"
author: Branson T Fausey
date: Sunday, 17th November, 2024 
output: html_notebook
---

```{r setup, include=FALSE}
# cleanup & stock the library shelves
rm(list = ls())
library(magrittr)
library(mosaic)
library(dcData)
library(openintro)
library(tidyverse)
library(tidyr)
library(manipulate)
library(esquisse)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(printr)
library(readr)
library(devtools)
library(lubridate)
library(leaflet)
library(foreign)
library(data.table)
library(base)
library(rvest)
library(tidytuesdayR)
library(usmap)
library(readxl)
set.seed(184)
```

___

# Research Question:

*How has Pennsylvania's deer population changed over time, and how does it compare to other states' populations?*

* For clarification, my main interest is the white-tailed deer species, but my analyses and descriptions will include other species of deer, mainly species native to the United States such as white-tailed and mule deer.

___

## Data Sources:

* [Deer Friendly](https://www.deerfriendly.com/)

* [Pennsylvania Deer Harvest 1915 to 2020](https://docs.google.com/spreadsheets/d/1C8gSJWomCEdPSvHPHm7UVd_oGQU6gmsm/edit?gid=1959951972#gid=1959951972)

* [US Deer Population Long-term Chart](https://docs.google.com/spreadsheets/d/1nuAUVkXsp1HkhIlPsiNFG_BzyO5HOYdS01jqrYXX-FY/edit?gid=1580702380#gid=1580702380)

* [Texas Deer Population 2000 to 2021](https://docs.google.com/spreadsheets/d/1GLy-Knmp_IzJALFd01E2bJCG8h0Ow3I4S9nCl7PDnbE/edit?gid=0#gid=0)

* [Nevada Mule Deer Population](https://docs.google.com/spreadsheets/d/1ZIL0-G_3x3nTbz_pz135ttUocQLy2OuIecnBJgdgpIM/edit?gid=0#gid=0)

___

Texas is reported to host the largest deer population in the country, while Nevada is reported to have the least amount of deer for a state in the contiguous US.

The PA and US data sources are cluttered with images and descriptions that follow no sense of data organization, so without changing any values, I simply remove the unnecessary  bits in the Excel files to import.

The TX and NV data sets can be read-in okay without adjustments.

___

```{r}
PAdeerharvest <- read_excel("PAdeerharvest.xlsx")
USdeerpop <- read_excel("USdeerpop.xlsx")
TXdeerpop <- read_excel("TXdeerpop.xlsx")
NVdeerpop <- read_excel("NVdeerpop.xlsx")
```







